Clean data

### 2021-10-15 analysis/02_clean-data.Rmd
De-packagify the project
Cleaned and finalized a dummy-coded (including brand) design and an index-coded design

```{r transform-design}
# Load design
design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
  select(-X1) %>%
  rename(
    version = question_set,
    task = question,
    alt = choice
  )

# Create the array for design X.
X <- array(
  data = NA,
  dim = c(
    nrow(data),             # Number of respondents.
    max(design$task),       # Number of choice tasks per respondent.
    (max(design$alt) + 1),  # Number of product alternatives per choice task.
    (ncol(design) - 3 + 1)  # Number of (estimable) attribute levels.
  )
)

# Reintroduce org1 and add the outside option coded as all zeros.
for (n in 1:dim(X)[1]) {
  # Filter for respondent n.
  X_n <- design %>% filter(version == data$version[n])
  for (s in 1:dim(X)[2]) {
    # Filter for task s and include placeholder for org1.
    X_s <- X_n %>%
      filter(task == s) %>%
      mutate(org1 = 0) %>%
      select(org1, org2:gov_rel3)
    for (p in 1:(dim(X)[3]-1)) {
      # Filter for task s and alt p orgs.
      X_p <- X_n %>%
        filter(task == s, alt == p) %>%
        select(org2:org4) %>%
        as_vector()
      # Fill in org1 to complte org intercept.
      X_s[p, "org1"] <- ifelse(sum(X_p) == 1, 0, 1)
    }
    # Save modified design, including outside option.
    X[n, s,,] <- rbind(X_s, rep(0, ncol(X_s))) %>% as.matrix()
  }
}
```

@@

```{r save-clean-data}
write_rds(data, here("data", "derived_data", "final_data.rds"))
write_rds(X, here("data", "derived_data", "final_design.rds"))
```

>>>>

```{r transform-design}
# Load the dummy design.
design <- read_csv(here::here("data", "derived_data", "dummy_design.csv")) %>%
  select(-`...1`) %>%
  rename(
    version = question_set,
    task = question,
    alt = choice
  )

# Create the arrays for a design with a brand intercept.
X <- array(
  data = NA,
  dim = c(
    nrow(data),             # Number of respondents.
    max(design$task),       # Number of choice tasks per respondent.
    (max(design$alt) + 1),  # Number of product alternatives per choice task.
    (ncol(design) - 3 + 1)  # Number of (estimable) attribute levels.
  )
)

# Reintroduce org1 and add the outside option coded as all zeros.
for (n in 1:dim(X)[1]) {
  # Filter for respondent n.
  X_n <- design %>% filter(version == data$version[n])
  for (s in 1:dim(X)[2]) {
    # Filter for task s and include placeholder for org1.
    X_s <- X_n %>%
      filter(task == s) %>%
      mutate(org1 = 0) %>%
      select(org1, org2:gov_rel3)
    for (p in 1:(dim(X)[3]-1)) {
      # Filter for task s and alt p orgs.
      X_p <- X_n %>%
        filter(task == s, alt == p) %>%
        select(org2:org4) %>%
        as_vector()
      # Fill in org1 to complete org intercept.
      X_s[p, "org1"] <- ifelse(sum(X_p) == 1, 0, 1)
    }
    # Save modified design, including outside option.
    X[n, s,,] <- rbind(X_s, rep(0, ncol(X_s))) %>% as.matrix()
  }
}

# Load the index design.
index_design <- read_csv(here::here("data", "derived_data", "index_design.csv")) %>%
  select(-`...1`) %>%
  rename(
    version = question_set,
    task = question,
    alt = choice
  )

# Create the arrays for the fully dummy and index designs.
X_dummy <- array(
  data = NA,
  dim = c(
    nrow(data),             # Number of respondents.
    max(design$task),       # Number of choice tasks per respondent.
    (max(design$alt) + 1),  # Number of product alternatives per choice task.
    (ncol(design) - 3)      # Number of (estimable) attribute levels.
  )
)

X_index <- array(
  data = NA,
  dim = c(
    nrow(data),                  # Number of respondents.
    max(index_design$task),      # Number of choice tasks per respondent.
    (max(index_design$alt) + 1), # Number of product alternatives per choice task.
    ncol(index_design) - 3       # Number of (estimable) attribute levels.
  )
)

# Add the outside option coded as all zeros for the dummy and index designs.
for (n in 1:dim(X_dummy)[1]) {
  # Filter for respondent n.
  X_dummy_n <- design %>% filter(version == data$version[n])
  X_index_n <- index_design %>% filter(version == data$version[n])
  for (s in 1:dim(X_dummy)[2]) {
    # Filter for task s.
    X_dummy_s <- X_dummy_n %>% 
      filter(task == s) %>% 
      select(org2:gov_rel3)
    X_index_s <- X_index_n %>% 
      filter(task == s) %>% 
      select(org1:gov_rel3)
    # Save modified design, including outside option.
    X_dummy[n, s,,] <- rbind(X_dummy_s, rep(0, ncol(X_dummy_s))) %>% as.matrix()
    X_index[n, s,,] <- rbind(X_index_s, rep(0, ncol(X_index_s))) %>% as.matrix()
  }
}
```

@@

```{r save-clean-data}
write_rds(data, here("data", "derived_data", "final_data.rds"))
write_rds(X, here("data", "derived_data", "final_design.rds"))
write_rds(X_dummy, here("data", "derived_data", "final_design_dummy.rds"))
write_rds(X_index, here("data", "derived_data", "final_design_index.rds"))
```
